Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-14 ms.qmd
Wrote opportunity for sleection paragraph

  # Calculated weighted mean by sample size. 
    f_cvr_mean <- (f_acute_cvr*N[1,"n"][[1]] + f_acclim_cvr*N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
    m_cvr_mean <- (m_acute_cvr*N[3,"n"][[1]] + m_acclim_cvr*N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
    t_cvr_mean <- (t_acute_cvr*N[5,"n"][[1]] + t_acclim_cvr*N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)

@@

### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*
```{r, wildlnRR10}
#| cache: true
#| include: false
#| echo: false
#| warning: false
#| 
#######################################
  ## lnRRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################

>>>>

  # Calculated weighted mean by sample size. 
    f_cvr_mean <- (f_acute_cvr * N[1,"n"][[1]] + f_acclim_cvr * N[2,"n"][[1]]) / sum(N[1:2, "n"]); pmcmc(f_cvr_mean)
    m_cvr_mean <- (m_acute_cvr * N[3,"n"][[1]] + m_acclim_cvr * N[3,"n"][[1]]) / sum(N[3:4, "n"]); pmcmc(m_cvr_mean)
    t_cvr_mean <- (t_acute_cvr * N[5,"n"][[1]] + t_acclim_cvr * N[6,"n"][[1]]) / sum(N[5:6, "n"]); pmcmc(t_cvr_mean)

  # Lets now convert these to a %
  f_cvr_mean_ef  <- abs((exp(f_cvr_mean) - 1)*100) # ~8.4% reduction
  m_cvr_mean_ef  <- abs((exp(m_cvr_mean) - 1)*100) # ~15% reduction
  t_cvr_mean_ef  <- abs((exp(t_cvr_mean) - 1)*100) # ~30% reduction

@@

### *Does the opportunity for selection differ across terrestrial and aquatic ectotherms?*

The opportunity for selection, as captured by $lnCVR_{Q_{10}}$, showed a decrease across all habitat types but were especially pronouced in terrestrial and marine ectotherms. Overall, there was a `r mean(t_cvr_mean_ef)`% (95% CI: `r quantile(t_cvr_mean_ef, 0.025)[1]` to `r quantile(t_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(t_cvr_mean)`) reduction in variation in physiological rates for terrestrial ectotherms and a `r mean(m_cvr_mean_ef)`% (95% CI: `r quantile(m_cvr_mean_ef, 0.025)[1]` to `r quantile(m_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(m_cvr_mean)`) reduction in variation for marine ectotherms when temperatures increase by 10$\deg$C. In contrast, freshwater ectotherms exhibited a much smaller reduction in physiologiocal rate variance at high temperatures (`r mean(f_cvr_mean_ef)`%, 95% CI: `r quantile(f_cvr_mean_ef, 0.025)[1]` to `r quantile(f_cvr_mean_ef, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(f_cvr_mean)`).

```{r, wildlnRR10}
#| cache: true
#| include: false
#| echo: false
#| warning: false
#| 
#######################################
  ## lnRRQ10 from Wild Populations ##
#######################################
##################################################
  # Organise the data and prune tree
##################################################
